Financialisation of Commodity Markets \\\large{Co-movement Behind-the-Scenes}

### 2024-09-16 docs/paper.qmd
Harmonize equations syntax

$$Y_{t}^{OI}\equiv\left \{ \left \{ \overline{{OI}_{1}^{\Delta \%}}, \overline{{OI}_{2}^{\Delta \%}}, ..., \overline{{OI}_{n}^{\Delta \%}} \right \}, \geq \right \}$$

$\overline{{OI}_{j}^{\Delta \%}}=\frac{1}{26}\sum_{k=0}^{25}(\frac{{OI}_{j,t-k}}{{OI}_{j,t-k-1}} - 1)$  
$OI_{j,t}\equiv$ open interest at close of period $t$ on the front (nearby) contract for commodity $j$.

>>>>

$$Y_{t}^{OI}\equiv\left \{ \left \{ \overline{OI_{1}^{\Delta \%}}, \overline{OI_{2}^{\Delta \%}}, ..., \overline{OI_{n}^{\Delta \%}} \right \}, \geq \right \}$$

$\overline{OI_{j}^{\Delta \%}}=\frac{1}{26}\sum_{k=0}^{25}(\frac{OI_{j,t-k}}{OI_{j,t-k-1}} - 1)$  
$OI_{j,t}\equiv$ open interest at close of period $t$ on the front (nearby) contract for commodity $j$.

### 2024-09-16 docs/paper.tex
Harmonize equations syntax

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={financialisation of Commodity Markets},
  pdfauthor={Devraj Basu; Olivier Bauthéac},
  pdfkeywords={Commodity markets, Financialisation, Asset pricing},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{frontmatter}
\title{financialisation of Commodity Markets \\\large{Co-movement
Behind-the-Scenes} }
\author[1]{Devraj Basu%
\corref{cor1}%
}
 \ead{devraj.basu@strath.ac.uk} 
\author[1]{Olivier Bauthéac%
%
}
 \ead{olivier.bautheac@strath.ac.uk}

@@

\[Y_{t}^{OI}\equiv\left \{ \left \{ \overline{{OI}_{1}^{\Delta \%}}, \overline{{OI}_{2}^{\Delta \%}}, ..., \overline{{OI}_{n}^{\Delta \%}} \right \}, \geq \right \}\]

\(\overline{{OI}_{j}^{\Delta \%}}=\frac{1}{26}\sum_{k=0}^{25}(\frac{{OI}_{j,t-k}}{{OI}_{j,t-k-1}} - 1)\)\\
\(OI_{j,t}\equiv\) open interest at close of period \(t\) on the front
(nearby) contract for commodity \(j\).

@@

\caption{\label{tbl-correlations-periods}This table shows the average
time series \(R^{2}\) for models where the returns series for the twenty
four individual US commodities are independently regressed against
relative change in their own commercial hedging pressure (CHP) series as
well as against that in aggregate CHP, a market wide measure of CHP
which calculation method is discussed in section
Section~\ref{sec-methods}. Averages are calculated independently across
the whole cross-section of US traded commodity assets considered in the
study as well as across commodity sectors and subsectors for the four
periods of interest (past: 1997-2003; financialisation: 2004-2008;
crisis: 2008-2013; post-crisis: 2013-2018). The results are discussed in
section Section~\ref{sec-results}.}

@@

\caption{\label{tbl-correlations-years}This table shows the average
pairwise correlation coefficients calculated independently across the
whole cross-section of commodity assets considered in the study as well
as across countries and commodity sectors and subsectors by year for the
whole periods of interest (1997-2018). For each year, the results are
calculated independently over the entire year as well as over phases of
aggregate backwardation and contango. Aggregate CHP construction and
corresponding regime definitions are discussed in section
Section~\ref{sec-methods} while the results are discussed in section
Section~\ref{sec-results}.}

>>>>

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Financialisation of Commodity Markets},
  pdfauthor={Devraj Basu; Olivier Bauthéac},
  pdfkeywords={Commodity markets, Financialisation, Asset pricing},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{frontmatter}
\title{Financialisation of Commodity Markets \\\large{Co-movement
Behind-the-Scenes} }
\author[1]{Devraj Basu%
\corref{cor1}%
}
 \ead{devraj.basu@strath.ac.uk} 
\author[1]{Olivier Bauthéac%
%
}
 \ead{olivier.bautheac@strath.ac.uk}

@@

\[Y_{t}^{OI}\equiv\left \{ \left \{ \overline{OI_{1}^{\Delta \%}}, \overline{OI_{2}^{\Delta \%}}, ..., \overline{OI_{n}^{\Delta \%}} \right \}, \geq \right \}\]

\(\overline{OI_{j}^{\Delta \%}}=\frac{1}{26}\sum_{k=0}^{25}(\frac{OI_{j,t-k}}{OI_{j,t-k-1}} - 1)\)\\
\(OI_{j,t}\equiv\) open interest at close of period \(t\) on the front
(nearby) contract for commodity \(j\).

@@

\caption{\label{tbl-correlations-periods}This table shows the average
pairwise correlation coefficients calculated independently across the
whole cross-section of commodity assets considered in the study as well
as across countries and commodity sectors and subsectors for the four
periods of interest (past: 1997-2003; financialisation: 2004-2008;
crisis: 2008-2013; post-crisis: 2013-2018). For each period, the results
are calculated independently over the entire period as well as over
phases of aggregate backwardation and contango. Aggregate CHP
construction and corresponding regime definitions are discussed in
section Section~\ref{sec-methods} while the results are discussed in
section Section~\ref{sec-results}.}

@@

\caption{\label{tbl-correlations-years}This table shows the average
pairwise correlation coefficients calculated independently across the
whole cross-section of commodity assets considered in the study as well
as across countries and commodity sectors and subsectors by year for the
whole period of interest (1997-2018). The results are discussed in
section Section~\ref{sec-results}.}
